%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeDevHeading}[1]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Chenkai Weng} \\ \vspace{1pt}
    \small +1-224-307-3331 $|$ \href{mailto:ckweng@u.northwestern.edu}{chenkai.weng@asu.edu} $|$ 
    \href{https://ckweng.github.io}{ckweng.github.io}
    %\href{https://www.linkedin.com/in/chenkai-weng/}{linkedin.com/in/chenkai-weng}
\end{center}

%-----------EDUCATION-----------
\section{Research Interests}
  \resumeSubHeadingListStart
  \item{\small{Applied cryptography with a focus on secure multi-party computation and zero-knowledge proofs.
    The design, analysis, and implementation of MPC (e.g., garbled circuits, oblivious transfer, homomorphic encryption, and secret sharing-based protocols) and ZKP protocols (VOLE-based ZK and non-interactive ZK).
    The building of secure systems by applying cryptography-based privacy-enhancing techniques to various fields, including databases, networking, formal verification, machine learning, health care, and decentralized systems.}}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northwestern University}{Evanston, IL}
      {PhD in Computer Science; Advisor: Xiao Wang}{Sept. 2019 -- Aug. 2024}
    %\resumeSubheading
      %{Northwestern University}{Evanston, IL}
      %{MSc Computer Science}{Sept. 2019 -- June 2023}
    \resumeSubheading
      {Xidian University}{Xi'an, China}
      {BSc in Information Security}{Sept. 2015 -- June 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Assistant Professor}{Tempe, AZ}
      {Arizona State University}{Starting Aug. 2024}

    %\resumeSubheading
      %{Research Assistant}{Evanston, IL}
      %{Northwestern University}{Sept. 2020 -- Present}
      %\resumeItemListStart
        %\resumeItem{Secure multi-party computation, zero-knowledge proof, cryptographic applications.}
        %\resumeItem{development of an NSF grant (co-lead).}
      %\resumeItemListEnd
    \resumeSubheading
      {Research Assistant}{Evanston, IL}
      {Northwestern University (advisor: Xiao Wang)}{Sept. 2020 -- Aug. 2024}

    \resumeSubheading
      {AI Research Summer Associate}{New York, NY}
      {JPMorgan Chase (mentor: Antigoni Polychroniadou)}{Jun. 2023 -- Sept. 2023}
      %\resumeItemListStart
        %\resumeItem{Privacy-preserving linear programming, designated multi-verifier zero-knowledge proofs.}
      %\resumeItemListEnd

    \resumeSubheading
      {Research Intern}{Remote}
      {Chainlink Lab (mentor: Dahlia Malkhi)}{Oct. 2022 -- May. 2023}
      %\resumeItemListStart
        %\resumeItem{Design and development of decentralized oracle system.}
      %\resumeItemListEnd

    \resumeSubheading
      {AI Research Summer Associate}{New York, NY}
      {JPMorgan Chase (mentor: Antigoni Polychroniadou)}{Jun. 2022 -- Sept. 2022}
      %\resumeItemListStart
        %\resumeItem{Research on dishonest-majority maliciously-secure multi-party computation protocol.}
      %\resumeItemListEnd

    \resumeSubheading
      {Research Intern}{Remote}
      {Microsoft Research (mentor: Melissa Chase)}{May. 2021 -- Jul. 2021}
      %\resumeItemListStart
        %\resumeItem{Design and development of private aggregation protocol from MPC and differential privacy.}
      %\resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    \resumeSubheading
      {Security Engineering Intern}{Beijing, China}
      {Alibaba Group (Mentor: Cheng Hong)}{July 2018 -- Jan. 2019}
      %\resumeItemListStart
        %\resumeItem{Secure multi-party computation, threshold cryptography, order-revealing encryption.}
      %\resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Articles in refereed conferences}
    %\resumeSubHeadingListStart
%{\small $\ast$ indicates alphabetical order}
\begin{enumerate}[leftmargin=0.20in]
  \item
    {\textbf{\small Dishonest Majority Constant-Round MPC with Linear Communication from DDH}} \\
		{\small Vipul Goyal, Junru Li, Ankit Kumar Misra, Rafail Ostrovsky, Yifan Song, Chenkai Weng \vspace{-2pt}}
		{\small International Conference on the Theory and Application of Cryptology and Information Security (Asiacrypt), 2024}
  \item
    {\textbf{\small Precio: Private Aggregate Measurement via Oblivious Shuffling}} \\
		{\small F. Betül Durak, Chenkai Weng, Erik Anderson, Kim Laine, Melissa Chase \vspace{-2pt}}
		{\small ACM Conference on Computer and Communications Security (CCS), 2024}
  \item
    {\textbf{\small Multi-Verifier Zero-Knowledge Proofs for Any Constant Fraction of Corrupted Verifiers}} \\
		{\small Daniel Escudero, Antigoni Polychroniadou, Yifan Song, Chenkai Weng \vspace{-2pt}}
		{\small ACM Conference on Computer and Communications Security (CCS), 2024}
  \item 
    {\textbf{\small Privacy-Preserving Regular Expression Matching using Nondeterministic Finite Automata}} \\
		{\small Ning Luo, Chenkai Weng, Jaspal Singh, Gefei Tan, Ruzica Piskac, Mariana Raykova \vspace{-2pt}}
		{\small European Symposium on Research in Computer Security (ESORICS), 2024}
  \item
    {\textbf{\small Scalable Zero-knowledge Proofs for Non-linear Functions in Machine Learning}} \\
		{\small Meng Hao, Hanxiao Chen, Hongwei Li, Chenkai Weng, Yuan Zhang, Haomiao Yang, Tianwei Zhang \vspace{-2pt}} \\
		{\small USENIX Security Symposium, 2024}
  \item
    {\textbf{\small ZKSQL: Verifiable and Efficient Query Evaluation with Zero-Knowledge Proofs}} \\
		{\small Xiling Li, Chenkai Weng, Yongxin Xu, Xiao Wang, Jennie Rogers \vspace{-2pt}} \\
    {\small Very Large Data Bases (VLDB), 2023}
  \item
    {\textbf{\small SUPERPACK: Dishonest Majority MPC with Constant Online Communication}} \\
		{\small Daniel Escudero, Vipul Goyal, Antigoni Polychroniadou, Yifan Song, Chenkai Weng \vspace{-2pt}} \\
    {\small Annual International Conference on the Theory and Applications of Cryptology and Information Security (Eurocrypt), 2023}
  \item
    {\textbf{\small AntMan: Interactive Zero-Knowledge Proofs with Sublinear Communication}} \\
		{\small Chenkai Weng, Kang Yang, Zhaomin Yang, Xiang Xie, and Xiao Wang \vspace{-2pt}} \\
		{\small ACM Conference on Computer and Communications Security (CCS), 2022}
  \item
    {\textbf{\small Constant-Overhead Zero-Knowledge for RAM Programs}} \\
		{\small Nicholas Franzese, Jonathan Katz, Steve Lu, Rafail Ostrovsky, Xiao Wang, Chenkai Weng \vspace{-2pt}} \\
		{\small ACM Conference on Computer and Communications Security (CCS), 2021}
  \item
    {\textbf{\small Mystique: Efficient Conversions for Zero-Knowledge Proofs with Applications to Machine Learning}} \\
		{\small Chenkai Weng, Kang Yang, Xiang Xie, Jonathan Katz, Xiao Wang \vspace{-2pt}} \\
		{\small USENIX Security Symposium, 2021}
  \item
	  {\textbf{\small Quicksilver: Efficient and Affordable Zero-Knowledge Proofs for Circuits and Polynomials over Any Field}} \\
		{\small Kang Yang, Pratik Sarkar, Chenkai Weng, Xiao Wang \vspace{-2pt}} \\
		{\small ACM Conference on Computer and Communications Security (CCS), 2021} \\
    {\small \textbf{Best Paper Award runner-up}}
  \item
    {\textbf{\small Wolverine: Fast, Scalable, and Communication-Efficient Zero-Knowledge Proofs for Boolean and Arithmetic Circuits}} \\
		{\small Chenkai Weng, Kang Yang, Jonathan Katz, Xiao Wang \vspace{-2pt}} \\
		{\small IEEE Symposium on Security and Privacy (Oakland), 2021}
  \item
          {\textbf{\small Developing High Performance Secure Multi-Party Computation Protocols in Healthcare: A Case Study of Patient Risk Stratification}} \\
		{\small Xiao Dong, David Randolph, Chenkai Weng, Abel Kho, Jennie Rogers, Xiao Wang \vspace{-2pt}} \\
		{\small AMIA Informatics Summit, 2021}
  \item
          {\textbf{\small Ferret: Fast Extension for coRRElated oT with small communication}} \\
		{\small Kang Yang, Chenkai Weng, Xiao Lan, Jiang Zhang, Xiao Wang\vspace{-2pt}} \\
		{\small ACM Conference on Computer and Communications Security (CCS), 2020}
  \item
          {\textbf{\small Better Concrete Security for Half-Gates Garbling (in the Multi-Instance Setting)}} \\
		{\small Chun Guo, Jonathan Katz, Xiao Wang, Chenkai Weng, Yu Yu\vspace{-2pt}} \\ 
		{\small International Cryptology Conference (CRYPTO), 2020}
\end{enumerate}
          %\resumeItemListStart
            %\resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
            %\resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
            %\resumeItem{Visualized GitHub data to show collaboration}
            %\resumeItem{Used Celery and Redis for asynchronous tasks}
          %\resumeItemListEnd
      %\resumeProjectHeading
          %{\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
          %\resumeItemListStart
            %\resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
            %\resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
            %\resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
            %\resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
          %\resumeItemListEnd
    %\resumeSubHeadingListEnd

%-----------Manuscripts-----
\section{Journal articles}
    %\resumeSubHeadingListStart
\begin{enumerate}[leftmargin=0.20in]
  \item 
    {\textbf{\small An Efficient ZK Compiler from SIMD Circuits to General Circuits}} \\
		{\small Dung Bui, Haotian Chu, Geoffroy Couteau, Xiao Wang, Chenkai Weng, Kang Yang, Yu Yu \vspace{-2pt}}
		{\small The Journal of Cryptology (JoC)}
  \item
    {\textbf{\small More Efficient Secure Matrix Multiplication for Unbalanced Recommender Systems}} \\
		{\small Zhicong Huang, Cheng Hong, Wen-jie Lu, Chenkai Weng, Hunter Qu \vspace{-2pt}} \\
		{\small IEEE Transactions on Dependable and Secure Computing (TDSC)}
\end{enumerate}

\section{Grants \& Awards \& Fellowships}
\begin{enumerate}[leftmargin=0.20in]
  \item Co-lead the development of an NSF grant (CNS Core: Medium: Privacy-Preserving and Censorship-Resistant Domain Name System)
  \item JPMorgan PhD Fellowship 2023.
  \item Northwestern Terminal Year Fellowship 2023-24.
    \item Runner-up for Best Paper Awards, ACM Conference on Computer and Communications Security (CCS) 2021.
    \item NUCS PhD Student Research Award, 2020-21.
\end{enumerate}


\section{Teaching}
  \resumeSubHeadingListStart

     \resumeSubheading
      {Co-lecturer}{Evanston, IL}
      {Northwestern University}{Jan. 2023 -- Mar. 2023}
      \resumeItemListStart
        \resumeItem{COMP\_SCI 496: Advanced Topics in Modern cryptography}
      \resumeItemListEnd

     \resumeSubheading
      {Teaching Assistant}{Evanston, IL}
      {Northwestern University}{Sept. 2020 -- Dec. 2020}
      \resumeItemListStart
        \resumeItem{COMP\_SCI 307: Introduction to Cryptography}
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------Talks-----------
\section{Invited Talks}
    %\resumeSubHeadingListStart
\begin{enumerate}[leftmargin=0.20in]
  \item
    \small May. and Oct. 2023 - SUPERPACK: Dishonest Majority MPC with Constant Online Communication, at NYU Crypto reading group, UPenn Security Seminar and CMU Cylab Crypto Seminar.
  \item
    \small Apr. 2023 - Efficient and Scalable Zero-Knowledge Proofs based on Vector Oblivious Linear Evaluation, at JPMorgan AlgoCRYPT Seminar.
  \item
	  \small Sept. 2022 - Efficient Interactive Zero Knowledge Proof Based on VOLE, at Yale University CS talk.
  \item
	  \small Mar. 2021 - Fast, Scalable, and Communication-Efficient Zero-Knowledge Proofs, Security and privacy seminar at Duke Univeristy.
\end{enumerate}

\section{Service}
\begin{enumerate}[leftmargin=0.15in, label={}]
  \item \textbf{Program committee member}: AsiaCCS 2024, CCS 2024, Usenix Security 2025, Euro S\&P 2025, CT-RSA 2025.
  \item \textbf{External reviewer}: CRYPTO 2021-23, ITC 2022, Asiacrypt 2022-23, IEEE S\&P (Oakland) 2023, PKC 2023.
    \item \textbf{Journal reviewer}: IEEE TDSC, IEEE TIFS, IEEE TCBB, ACM TOPS, IACR JoC.
\end{enumerate}
%
%-----------PROGRAMMING SKILLS-----------
\section{Software}
 \begin{enumerate}[leftmargin=0.15in, label={}]
   \item \textbf{EMP library}: EMP-TOOL (Circuits for floating-point arithmetic, various fundamental cryptographic primitives), EMP-OT (Oblivious transfer based on VOLE), EMP-ZK (Interactive zero-knowledge proofs based on VOLE, including the circuit, polynomial and RAM models).
   \item \textbf{SUPERPACK}: An actively-secure dishonest-majority MPC protocol based on packed Shamir secret sharing.
 \end{enumerate}


%-------------------------------------------
\end{document}

